LAGOS lake depth

### 2020-03-24 README.Rmd
better link text
title adjustment

## Bathymetry data from thousands of lakes show that difficulty modeling in-lake slope limits lake depth prediction

@@

Data: [bathymetry derived lake geometry](data/depth_predictors.csv)

>>>>

## Bathymetry data from thousands of lakes show that difficulty modeling in-lake slope confounds lake depth prediction

@@

Data: [bathymetry derived depth predictors](data/depth_predictors.csv)
